Spring haul-out behavior of seals in the Bering and Chukchi seas

### 2024-01-29 analysis/paper/London_HauloutBeahvior.Rmd
update caption for spatial data map/figure
update to spatial distribution figure caption

Figure \@ref(fig:dataMap) shows the
spatial distribution of weighted locations with available haul-out behavior data
used for analysis of each species across the study area.

@@

(ref:mapCaption) Spatial distribution of haul-out records during the months of March through July 15 for each of the three species. Linking location estimates with haul-out records in space and time allows for inclusion of weather covariates in the final model. For this visualization, data were collated across all years between 2005 and 2020 and each hexagonal cell represents an area of 50 km^2^

```{r dataMap, include=TRUE, fig.cap="(ref:mapCaption)"}

@@

ggplot() +
  annotation_spatial(world,
                     linewidth = 0,
                     fill = "grey80") +
  layer_spatial(
    data = locs_count,
    aes(fill = ct),
    linewidth = 0.1,
    color = "grey75"
  ) +
  scico::scale_fill_scico(
    palette = "imola",
    trans = "log10",
    aesthetics = "fill",
    name = "number of locations",
    guide = guide_colorbar(
      title.position = "bottom",
      barwidth = 15,
      barheight = 0.5,
      title.hjust = 0.5
    )
  ) +
  facet_grid( ~ species) +
  labs(
    title = "Spatial distribution of haul-out behavior records",
    subtitle = "Location estimates were linked by time with haul-out records. 
    Data are shown collated across 2005-2020 between 01 March-15 July
    for each of the three species.",
    caption = "One hexagonal cell represents 50 km^2^"
  ) +
  theme(
    legend.position = "bottom"
  )
```

>>>>

Figure \@ref(fig:dataMap) shows the spatial distribution of weighted locations
with available haul-out behavior data used for analysis of each species across
the study area. Figure \@ref(fig:dataCal) shows the temporal distribution of all
haul-out data across the study season for each species. Observations for ribbon
and spotted seals were concentrated in the months of May and June due to the
timing of deployment (April and May) and the timing of molt (May and June).
During molt, seals (and their attached bio-loggers) spend more time out of the
water and more data are transmitted. Molt timing also impacts when many
deployments end as any bio-loggers adhered to the hair will fall off. Relative
to the other species in the study, there were fewer deployments of bio-loggers
on bearded seals. This resulted in fewer data observations overall and
noticeably lower in numbers May and June. The majority of bearded seal
deployments started later in the summer and, by May, bio-loggers had either
fallen off or their batteries were depleted.

@@

(ref:mapCaption) **Spatial distribution of haul-out records from 1 March through July 15 for each of the three species.** \linebreak Linking location estimates with haul-out records in space and time allows for inclusion of weather covariates in the final model. For this visualization, data were collated across all years between 2005 and 2020 and each hexagonal cell represents an area of 50 km^2^

```{r dataMap, include=TRUE, fig.asp = 0.5, fig.cap="(ref:mapCaption)"}

@@

ggplot() +
  annotation_spatial(world,
                     linewidth = 0,
                     fill = "grey80") +
  layer_spatial(
    data = locs_count,
    aes(fill = ct),
    linewidth = 0.1,
    color = "grey75"
  ) +
  scico::scale_fill_scico(
    palette = "imola",
    trans = "log10",
    aesthetics = "fill",
    name = "number of locations",
    guide = guide_colorbar(
      title.position = "bottom",
      barwidth = 15,
      barheight = 0.5,
      title.hjust = 0.5
    )
  ) +
  facet_grid( ~ species) +
  labs(
    caption = "One hexagonal cell represents 50 km^2^"
  ) +
  theme(
    legend.position = "bottom"
  )
```
